---
title: "Statistical Analaysis"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---

The statistical significance of differences between groups has been evaluated using one-way ANOVA, followed by Dunnett's test to compare treatment groups to the control and Tukey's test to compare groups to each other.  The analysis has been performed using the Multcomp package for R.  

### Groups
```{r echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}
source('decorporationData.R')
library(knitr)
library(pander)
groups <- dcast(mreten[which(mreten$Location == "Retained"), ], Group+Ligand+Time~Value, mean)[,1:3]
kable(cbind(groups, Treatment = '100 umol / kg'))


```




### Total retained 
```{r echo=FALSE}
fit <- aov(Body ~ Group, data = reten)
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))


#fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "ART"), ])
#summary(fit)
#pander(print(summary(glht(fit, linfct=mcp(Group="Dunnett")))))
#summary(glht(fit, linfct=mcp(Group="Tukey")))





#tbdata <- ddply(mdata[ which(mdata$variable != 'NA'), ], .(Group, Ligand, Time, variable), summarize, Mean = mean(value), 
#                SD = sd(value))
#tbdata <- dcast(mdata[ which(mdata$variable != 'NA'), ], Group+Ligand+Time ~ variable, mean)
#kable(tbdata[,1:3])
#kable(dcast(mdata[ which(mdata$variable != 'NA'), ], Group+Ligand+Time ~ variable, mean))
#summary(glht(fit, linfct=mcp(Group="Dunnett")))
```

### Skeleton  
```{r echo=FALSE, warning=FALSE}
fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "Skeleton"), ])
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))
```

### Liver  
```{r echo=FALSE, warning=FALSE}
fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "Liver"), ])
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))
```

### Soft tissue  
```{r echo=FALSE, warning=FALSE}
fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "Soft"), ])
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))
```

### Abdominal tissue  
```{r echo=FALSE, warning=FALSE}
fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "ART"), ])
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))
```

### Kidney  
```{r echo=FALSE, warning=FALSE}
fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "Kidneys"), ])
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))
```

### Heart  
```{r echo=FALSE, warning=FALSE}
fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "Heart"), ])
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))
```

### Lungs
```{r echo=FALSE, warning=FALSE}
fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "Lungs"), ])
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))
```

### Spleen
```{r echo=FALSE, warning=FALSE}
fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "Spleen"), ])
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))
```

### Brain
```{r echo=FALSE, warning=FALSE}
fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "Brain"), ])
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))
```

### Thymus
```{r echo=FALSE, warning=FALSE}
fit <- aov(value ~ Group, data = mdata[ which(mdata$variable == "Thymus"), ])
summary(glht(fit, linfct=mcp(Group="Dunnett")))
summary(glht(fit, linfct=mcp(Group="Tukey")))
```